Boosted Mirror Descent, Frank-Wolfe, and Herding

### 2013-10-04 icml/herding-connection.tex
lots of minor fixes

The above updates correspond to \dual for $U = \sX$, $\Theta = \sH$, 
$\alpha_t = 1$, $h \equiv 0$, 
$R(\theta) = \ip{\bar{\phi}}{\theta} + \frac{1}{2}\|\theta\|_{\sH}^2$, 
and $\imath(u)$ the canonical extension of $\phi$ from $\sX$ to $\Delta_{\sX}$.
To see this, note that 
\begin{align}
\lefteqn{\arg\min_{\theta \in \sH} \ip{\imath(u)}{\theta} - R(\theta)} \\
 &= \arg\min_{\theta \in \sH} \ip{\bE_{u}[\phi(x)]-\bar{\phi}}{\theta} - \frac{1}{2}\|\theta\|_{\sH}^2 \\
 &= \bE_u[\phi(x)] - \bar{\phi}.
\end{align}
For $u = 0$, this gives us the first bullet point. For $u = \hat{u}_t$, 
this gives us the third bullet point. Finally, the second bullet point 
is already in the form given in \dual.

@@

If we do not restrict $\alpha_{t}$ to be 1, we obtain a class of algorithms
we call {\em $\alpha_{t}$-weighted herding}. For the $t$-weighted herding 
algorithm with we obtain a stronger bound of $\frac{8r^2}{T}$ instead.

\subsection{Herding in Infinite Dimensions}
\label{sec:infinite-case}

>>>>

The above updates correspond to \dual for $U = \Delta_{\sX}$, $\Theta = \sH$, 
$\ip{u}{\theta} = \ip{\bE_u[\phi(x)]}{\theta}_{\sH}$, $\alpha_t = 1$, $h \equiv 0$, and
$R(\theta) = \ip{\bar{\phi}}{\theta}_{\sH} + \frac{1}{2}\|\theta\|_{\sH}^2$.
To see this, note that 
\begin{align}
\lefteqn{\arg\min_{\theta \in \sH} \ip{u}{\theta} - R(\theta)} \\
 &= \arg\min_{\theta \in \sH} \ip{\bE_{u}[\phi(x)]-\bar{\phi}}{\theta}_{\sH} - \frac{1}{2}\|\theta\|_{\sH}^2 \\
 &= \bE_u[\phi(x)] - \bar{\phi}.
\end{align}
For $u = 0$, this gives us the first bullet point. For $u = \hat{u}_t$, 
this gives us the third bullet point. Finally, the second bullet point 
is already in the form given in \dual.

@@

If we do not restrict $\alpha_{t}$ to be 1, we obtain a class of algorithms
we call {\em $\alpha_{t}$-weighted herding}. For the $\alpha_t = t$ we obtain 
a stronger bound of $\frac{8r^2}{T}$.

\subsection{$q$-herding}
\label{sec:infinite-case}
